Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
more intro trimming

Tor is primarily known as an anonymity tool. In fact, it is the most widely used anonymity tool today. 
However, there are complaints that Tor is not usable. Norcie~\cite{norcie2012eliminating} did an experiment which identified stopping points in Tor browser, 
finding out when people would get frustrated with Tor so much they would stop using it. 
%redo this next couple sentences into something better
To our knowledge, that has been the only user study of Tor. 
Since then, Tor has had a lot of updates. 
Additionally, there were a lot of features that were untested. 
There have been been no major usability evaluations of
Tor Browser since the introduction of the 4.0 series,
which introduced radical UI changes.

We briefly describe the results of a completed study
that examined the download, installation, and basic browsing behaviors.
This study uncovered a number of bugs and stopping points
which has already effected concrete change in the browser.

We ran a small pilot study of five journalists which involved a talk-aloud in which 
participants explained the motivation for their actions and any confusion that they had during the process. 
We recorded what they were saying out loud in their cognitive walk through,
and later added these words to the screen videos as subtitles.
We did this to find new stopping points, and sources of confusion. 
But in the process, we were also able to observe how users would download Tor, 
if they could understand the address bar/menu, how well they were able to complete basic tasks
(searching, setting new circuits, etc.), and generally if they had any usability complaints about the browser. 
The participants also took an exit survey which estimated their familiarity with technology and security.

 On average, participants took 26 minutes to complete the study ($\sigma = 7$~min).  The result was that people did have difficulty with installing Tor Browser (principally because of the Gatekeeper code-signing feature on OS~X), did not understand what many of the many options meant, and were confused about why certain things were happening.

>>>>

Tor is primarily known as an anonymity tool. In fact, it is the most widely used anonymity tool today. 
However, there are complaints that Tor is not usable. Norcie~\cite{norcie2012eliminating} did an experiment which identified stopping points in Tor browser, 
finding out when people would get frustrated with Tor so much they would stop using it. 
%redo this next couple sentences into something better
To our knowledge, that has been the only user study of Tor. 
Since then, Tor has had a lot of updates. 
Additionally, there were a lot of features that were untested. 
There have been been no major usability evaluations of
Tor Browser since the introduction of the 4.0 series,
which introduced radical UI changes. We ran a small pilot study 
of five journalists. This study uncovered a number of bugs and 
stopping points which has already effected concrete change in the browser.
